stats-project

### 2020-12-04 R - Deliverable/MSDS 6371 - Project.Rmd
add scaling and new variables to q2

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
summary(data_train)
summary(data_test)

@@

train_data_q2 = data_train %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  SalePrice)
train_data_q2$GrLivArea2 = train_data_q2$GrLivArea^2
train_data_q2 = train_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2, SalePrice)

@@

test_data_q2 = data_test %>%  select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual,  YearRemodAdd, GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr, Remodel,OverallQual)
test_data_q2$GrLivArea2 = test_data_q2$GrLivArea^2
test_data_q2 = test_data_q2 %>% select(Id, GrLivArea, Neighborhood, LotArea, YrSold, SaleCondition, HouseStyle, KitchenQual, YearRemodAdd,GarageCars, PoolArea, Fireplaces,BsmtFullBath,BsmtHalfBath,FullBath,HalfBath,BedroomAbvGr,Remodel,OverallQual,  GrLivArea2)
test_data_q2 =  predict(train_data_q2_process, test_data_q2)

@@

#look for missing values
missing.values <- test_data_q2 %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing))

@@

                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*GrLivArea2 +

                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd )*LotArea +

                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd ) * BedroomAbvGr

>>>>

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
summary(data_train)
summary(data_test)

@@

selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "PoolArea", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")

train_data_q2 = data_train %>% select(Id, selected_features_q2,  SalePrice)

@@

test_data_q2 = data_test %>%  select(Id, selected_features_q2)
test_data_q2 =  predict(train_data_q2_process, test_data_q2)

@@

#look for missing values
missing.values <- train_data_q2 %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing))

@@

                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer+KitchenQual_Ex+KitchenQual_Fa+KitchenQual_Gd)*GrLivArea2 +

                 (Neighborhood_Blmngtn+Neighborhood_BrDale+Neighborhood_ClearCr+Neighborhood_CollgCr+Neighborhood_Crawfor+Neighborhood_Edwards+Neighborhood_Gilbert+Neighborhood_IDOTRR+Neighborhood_MeadowV+Neighborhood_Mitchel+Neighborhood_NAmes+Neighborhood_NPkVill+Neighborhood_NridgHt+Neighborhood_NWAmes+Neighborhood_OldTown+Neighborhood_Sawyer+Neighborhood_SawyerW+Neighborhood_Somerst+Neighborhood_StoneBr+Neighborhood_SWISU+Neighborhood_Timber+Neighborhood_Veenker+SaleCondition_Abnorml+SaleCondition_AdjLand+SaleCondition_Alloca+SaleCondition_Family+SaleCondition_Normal+HouseStyle_1.5Fin+HouseStyle_1.5Unf+HouseStyle_1Story+HouseStyle_2.5Unf+HouseStyle_2Story+HouseStyle_SFoyer)*LotArea
